Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-19 Manuscript_draft.Rmd
update table1

table2 <- as_grouped_data(Q2_1_table, groups = "setting")

table2 %>% 
  as_flextable() %>% 
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()

>>>>

table2 <- as_grouped_data(Q2_1_table, groups = "setting")
table2 <- flextable(table2)
table2 <- table2 %>%
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()
table2 <- width(table2, width = 10)
table2

Q2_1_table <- Q2_1_table %>%
  arrange(setting)
table2 <- as_grouped_data(Q2_1_table, groups = "setting")
table2 %>%
  as_flextable() %>%
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
  theme_vanilla()
